%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper, 11pt]{article}

\usepackage{hyperref}
\usepackage{geometry}

%\usepackage[spanish]{babel}
%  \selectlanguage{english}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
%\usepackage[scaled]{uarial}
%\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
%\usepackage[T1]{fontenc}

% Set your name here
\def\name{George G. Vega}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://www.ggvega.com}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
%  body={6.5in, 9in},
  left=1.3cm,
  top=1in,
  right=1.3cm,
  bottom=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\sffamily\mdseries\Large}
%\subsectionfont{\sffamily\mdseries\itshape\large}

% Other possible font commands include:
% rmfamily
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0.45cm}
  }
}{
  \end{list}
}

% Para poder poner comandos genericos en tablas (en el inicio del argumento)
\usepackage{array}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \begin{tabular}{>{\bfseries}p{4cm}l}
    Mobile & +56 (9) 7 647 2552 \\
    e-mail & \href{mailto:g.vegayon@gmail.com}{\tt g.vegayon@gmail.com} \\
    website & \href{http://ggvega.com}{\tt http://ggvega.com} \\
  \end{tabular}
\end{minipage}

\section*{Personal Information}

\begin{minipage}{0.45\linewidth}
  \begin{tabular}{>{\bfseries}p{4cm}l}
  Date of birth & March 2, 1988.\\
  Place of birth & Iquique, Chile\\
%  Marital status  & Married\\
  Location & Santiago, Regi\'on Metropolitana, Chile.
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
\item {\bf Ph.D. in Social Science} (starting on fall 2014), California Institute of Technology (expected 2019) \\
{\bf Master in Economics and Public Policy}, Adolfo Ib\'a\~nez University (2011) \\
{\bf BS. in Business Administration}, Adolfo Ib\'a\~nez University (2010) \\
{\bf BS. in Social Sciences}, Adolfo Ib\'a\~nez University (2010) 
\end{itemize}

\section*{Work Experience}

\begin{itemize}
\item \textbf{Chilean Pension Supervisor, 2011--Present} Research Division \emph{Analyst}.
Conducting research and statistical analysis on the Unemployment Insurance System and the Pension System.
\item \textbf{Nodos Chile Social Network Analysis Ltda., 2012--Present} \emph{Partner}.
Founding partner of one of the first applied SNA Consultancy Entrepreneurships in Chile.
\item \textbf{Adolfo Ib\'a\~nez University, 2011--2012.} School of Government \emph{Adjunct Professor} of Economics and Statistical Computing (2012). 
Taught Introductory courses of Economics, Microeconomics and Statistical computing with Stata.
\item \textbf{Chilean Ministry of Social Planning, 2011.} Social Programs Monitoring \emph{Analyst}.
Survey and Analysis of the Government social programs supply and supporting the Monitoring Division with the Open-Data Initiative.
\end{itemize}

\section*{Research}

\subsection*{Publications and Work in progress}
\begin{itemize}
\item F\'abrega, J., \& {\bf Vega, G.} (2013) The impact of television rating over twitter activity: Evidence for Chile based on the Teleton 2012. In {\it Cuadernos.info}, 33. doi:10.7764/cdi.33.533.
%El impacto del rating televisivo sobre la actividad en Twitter: Evidencia para Chile
\item Repetto, A., \& {\bf Vega, G.} (2013). The impact of increasing retirement payroll-tax: Pensions, Salaries and Employment. In {\it Centro de Pol\'iticas Laborales, Adolfo Ib\'a\~nez University}.
\item {\bf Vega, G}, \& Melse, E. (2013). PARALLEL: multicore computing in Stata.
\item F\'abrega, J., Paredes, P., \& {\bf Vega, G.} (2013). Exploratory Analysis of Television Audience in Twitter. In {\it Informe Anatel 2013, chapter 5, National Television Asociation (ANATEL)}.
%\item ``blopmatching: Implementing bi-level optimization matching algorithm''.
\item Quintanilla, X., Poblete, I., \& {\bf Vega, G.} (2013). Actuarial Analysis on the Unemployment Insurance Funds. In {\it Working Paper N 56, Chilean Pension Supervisor}.
\item {\bf Vega, G.} (2013). Unitary Needed Capital (CNU): Computing and Introducing Stata module {\tt cnu}. In {\it Technical Notes, Chilean Pension Supervisor}.
%\item ``PIB Académico: Din\'amicas de la colaboración acad\'emica en Chile'', {\it Universidad Adolfo Ib\'a\~nez}
%\item ``Formaci\'on de la Opini\'on P\'ublica en los Medios Sociales'' en {\it Universidad Adolfo Ib\'a\~nez}.
\end{itemize}

\subsection*{Selected Software}
\begin{itemize}
\item {\bf Vega, G.}, \& Mu\~noz, E. (2013). ABCoptim: An Implementation of the Artificial Bee Colony (ABC) Optimization algorithm. In {\it The Comprehensive R Archive Network}.
\item {\bf Vega, G.} (2012). PARALLEL: Stata module for Parallel Computing. In {\it Statistical Software Components, Boston College Department of Economics}.
%\item ``blopmatching: Implementing a New Matching Estimator based on a Bi-Level Optimization Problem'', in development.
\item {\bf Vega, G.}, F\'abrega, J., \& Kunst, J. (2012). rgexf: An R package to build gexf graph files. In {\it The Comprehensive R Archive Network}.
\item {\bf Vega, G.}, \& Fajnzylber, E. (in development). NNMATCH2: A faster implementation of the Nearest Neighbour Matching Estimator.
\item {\bf Vega, G.} (2012). googlePublicData: An R package to build Google's Public Data Explorer DSPL Metadata files, In {\it The Comprehensive R Archive Network}.
\end{itemize}

\subsection*{Conferences and Presentations}

\begin{itemize}
\item ``PARALLEL: Stata module for parallel computing'', presented at the {\it Stata Conference} (2013), New Orleans, USA.
\item ``Introducing {\tt rgexf} and how to develop your own R-package'', presetented at the {\it Group of R users in Chile} (2013), Santiago, Chile.
\item ``Introducing PARALLEL: Stata Module for Parallel Computing'', presented at the {\it Reuni\'on Anual de la Sociedad de Economistas de Chile} (2012), Vi\~na del Mar, Chile.
\end{itemize}

% \begin{itemize}
%\item
%\href{https://gephi.org/2013/rgexf-an-r-library-to-work-with-gexf-graph-files/}{``rgexf: An R library to work with GEXF graph files''} in {\it Gephi Blog}, published in february 12, 2013.
%\item \href{http://www.elmostrador.cl/opinion/2012/04/04/aborto-en-twitter-un-debate-a-medias/}{``Aborto en Twitter: un debate a medias''} in {\it El Mostrador}, published in april 4, 2012.
%\item \href{http://www.uai.cl/200911165701/columna-de-opinion/columnas-opinion/reinventar-la-ciudadania-la-otra-campana-que-obama-esta-ganando}{``Reinventar la ciudadanía, la otra campaña que Obama está ganando''} in {\it El Mostrador}, published in november 10, 2009.
%\end{itemize}

\section*{Honours and Professional Achievements}

\begin{itemize}
\item \textbf{Fellowship} California Institute of Technology, for Ph.D. Programme in Social Sciences (Starting Fall 2014).
\item \textbf{Ad hoc reviewer} (parallel computing) of the Official Journal of The Society for Computational Economics (January 2013).
\item \textbf{Book reviewer} ``Network Graph Analysis and Visualization with Gephi'', by Ken Cherven, Packt Publishing, 2013.
\item \textbf{Founder of the R Users Group in Chile} Starting in January 2013.
\item \textbf{Honorable Mention} (Posters Sesion. Work: \emph{Introducing Parallel: Stata Module for Parallel Computing}) given by the Chilean Economics Society during its 2012 annual meetting.
\item \textbf{Honour Scholarship} given by Adolfo Ib\'a\~nez University for completing undergrad and graduate studies (2006-2010).
\item \textbf{Director and co-founder of the Project ``Educaci\'on Joven'', 2008--2009.} A program in remedial education
 dedicated to assist low income students on reaching Higher Education.
%\item \textbf{Software workshop, 2010.} \emph{Co-founder} of the workshop thaught by Economics and PP Masters's Students at Adolfo Ib\'a\~nez University in order to introduce grad students into scholar research software (\LaTeX, \emph{R}, Stata, etc.).
\end{itemize}

%\bigskip

% Footer
%\begin{center}
%  \begin{footnotesize}
%    last update: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}

