%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper, 11pt]{article}

\usepackage{hyperref}
\usepackage{geometry}

%\usepackage[sfdefault]{cabin}
%\usepackage[T1]{fontenc}

\usepackage[sfdefault]{overlock} %% Option 'sfdefault' only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}



% Set your name here
\def\name{George G. Vega Yon}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://ggvy.cl}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
%  body={6.5in, 9in},
  left=1.3cm,
  top=1in,
  right=1.3cm,
  bottom=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\sffamily\mdseries\Large}
%\subsectionfont{\sffamily\mdseries\itshape\large}

% Other possible font commands include:
% rmfamily
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0.45cm}
  }
}{
  \end{list}
}

% Para poder poner comandos genericos en tablas (en el inicio del argumento)
\usepackage{array}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \begin{tabular}{>{\bfseries}p{4cm}l}
    Mobile & +1 (626) 381 8171 \\
    e-mail & \href{mailto:g.vegayon@gmail.com}{\tt g.vegayon@gmail.com} \\
    website & \href{https://ggvy.cl}{\tt https://ggvy.cl} \\
    Code & \href{https://github.com/gvegayon}{\tt https://github.com/gvegayon}\\
    Linkedin & \href{https://www.linkedin.com/in/georgevegayon/}{\tt https://www.linkedin.com/in/georgevegayon/}
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize}
\item 
{\bf Ph.D. in Biostatistics (with concentration in Stat. Comp.)} University of Southern California (2017-2019, expected) \\
{\bf M.Sc. in Social Sciences (Economics)} California Institute of Technology (2016) \\
{\bf Master in Economics and Public Policy}, Adolfo Ib\'a\~nez University (2011) \\
{\bf BS. in Social Sciences} and {\bf BS. in Business Administration}, Adolfo Ib\'a\~nez University (2010)
\end{itemize}

\section*{Professional Experience}

\begin{itemize}
\item \textbf{University of Southern California, 2015--present} Department of Preventive Medicine \emph{Research Programmer}. Development and Implementation of statistical methods using R, funded by National Cancer Institute, NIH, and the US Department of Defense.
\item \textbf{Chilean Pension Supervisor, August 2011-- August 2014} Research Division \emph{Analyst}. Statistical and econometric analysis on the Chilean unemployment insurance, statistical software development, serving as a bridge between the IT and Research divisions.
\item \textbf{Nodos Chile Social Network Analysis Ltda., January 2012--January 2014} \emph{Partner}.
Founding partner of one of the first applied SNA Consultancy Entrepreneurship in Chile.
\item \textbf{Adolfo Ib\'a\~nez University, January 2011--June 2012.} School of Government \emph{Adjunct Professor}.
Taught Introductory courses of Economics, Microeconomics and Statistical computing with Stata.
\item \textbf{Chilean Ministry of Social Planning, March 2011--December 201.} Social Programs Monitoring \emph{Analyst}.
Survey and Analysis of the Government social programs supply and supporting the Monitoring Division with the Open-Data Initiative.
\end{itemize}

\section*{Software}

\begin{itemize}
\item[] R, C++, \LaTeX, SQL, XML, regex, Stata+Mata, VBA, Gephi, Pajek, Mathematica, MS Suit, git, unix
\end{itemize}

\section*{Research}

\subsection*{Selected Publications and Work in progress}
\begin{itemize}

\item Sensing Eating Mimicry Among Family Members. Accepted at {\it Transitional Behavioral Medicine}. With Brooke Bell, Kayla de la Haye, and others.
\item Network Influences on policy implementation: Evidence from a global health treaty. In {\it Social Science and Medicine}, 222. (2019) with Thomas W. Valente, Stephanie Pitts, and Heather Wipfli. 
\item On the Automatic Annotation of Gene Functions Using Observational Data and Phylogenetic Trees. Work in Progress. With Duncan C. Thomas, Paul Marjoram, and others.
\item Exponential Random Graph models for Little Networks, Work In Proggress. With de la Haye, Kayla.
\item Visualizing Large Annotated Graphs as Heatmaps, Work In Proggress. With Valente, TW.
\item The impact of television rating over twitter activity: Evidence for Chile based on the Teleton 2012. In {\it Cuadernos.info}, 33. doi:10.7764/cdi.33.533 (2013) With F\'abrega, J.
\item Parallel: Stata module for parallel computing. In review at {\it Stata Journal}. With Quistorff, B.
%El impacto del rating televisivo sobre la actividad en Twitter: Evidencia para Chile
\item The impact of increasing retirement payroll-tax: Pensions, Salaries and Employment. In {\it Centro de Pol\'iticas Laborales, Adolfo Ib\'a\~nez University} (2013). With Repetto, A.
%\item {\bf Vega, G}, \& Melse, E. (2013). PARALLEL: multicore computing in Stata.
\item Exploratory Analysis of Television Audience in Twitter. In {\it Informe Anatel 2013, chapter 5, National Television Asociation (ANATEL)} (2013). With F\'abrega, J., and Paredes, P.
%\item ``blopmatching: Implementing bi-level optimization matching algorithm''.
\end{itemize}

\subsection*{Selected Software}
\begin{itemize}
\item {\bf Vega Yon, G.} , Dyal, S., Hayes, T., Valente, T. (2016) ``netdiffuseR: Network Analysis for Diffusion of Innovations''. In {\it The Comprehensive R Archive Network}.
\item Rau, T., {\bf Vega Yon, G.} \& Espinoza, D. ``blopmatching: Implementing a New Matching Estimator based on a Bi-Level Optimization Problem'', (2014). Developed for Diaz, Rau and Rivera (RESTAT, 2015)
\item {\bf Vega Yon, G.}, \& Mu\~noz, E. (2013). ABCoptim: An Implementation of the Artificial Bee Colony (ABC) Optimization algorithm. In {\it The Comprehensive R Archive Network}.
%\item {\bf Vega Yon, G.} (2012). PARALLEL: Stata module for Parallel Computing. In {\it Statistical Software Components, Boston College Department of Economics}.
\item {\bf Vega Yon, G.}, F\'abrega, J., \& Kunst, J. (2012). rgexf: An R package to build gexf graph files. In {\it The Comprehensive R Archive Network}.
%\item {\bf Vega Yon, G.}, \& Fajnzylber, E. (in development). NNMATCH2: A faster implementation of the Nearest Neighbour Matching Estimator.
\end{itemize}

%\subsection*{Conferences and Presentations}
%
%\begin{itemize}
%\item ``PARALLEL: Stata module for parallel computing'', presented at the {\it Stata Conference} (2013), New Orleans, USA.
%\item ``Introducing {\tt rgexf} and how to develop your own R-package'', presetented at the {\it Group of R users in Chile} (2013), Santiago, Chile.
%\item ``Introducing PARALLEL: Stata Module for Parallel Computing'', presented at the {\it Reuni\'on Anual de la Sociedad de Economistas de Chile} (2012), Vi\~na del Mar, Chile.
%\end{itemize}

%\subsection*{Press and others}
%
% \begin{itemize}
%\item
%\href{https://gephi.wordpress.com/2013/02/12/rgexf-an-r-library-to-work-with-gexf-graph-files/}{``rgexf: An R library to work with GEXF graph files''} in {\it Gephi Blog}, published in february 12, 2013.
%\item \href{http://www.elmostrador.cl/opinion/2012/04/04/aborto-en-twitter-un-debate-a-medias/}{``Aborto en Twitter: un debate a medias''} in {\it El Mostrador}, published in april 4, 2012.
%\item \href{http://www.uai.cl/200911165701/columna-de-opinion/columnas-opinion/reinventar-la-ciudadania-la-otra-campana-que-obama-esta-ganando}{``Reinventar la ciudadanía, la otra campaña que Obama está ganando''} in {\it El Mostrador}, published in november 10, 2009.
%\end{itemize}

\section*{Honors and Professional Achievements}

\begin{itemize}
\item \textbf{Book reviewer}: ``Microeconometrics and Matlab: An Introduction'', by Adams, Clarke and Quinn, Oxford University Press, 2015. ``Mastering Gephi Network Visualization'', by Ken Cherven, Packt Publishing, 2015. ``Network Graph Analysis and Visualization with Gephi'', by Ken Cherven, Packt Publishing, 2013.
\item \textbf{Awards} Fellowship, California Institute of Technology, for Ph.D. Programme in Social Sciences, 2014. Scholarship, Adolfo Ib\'a\~nes University, for Undergraduate and Graduate Studies (2006).
%\item \textbf{Book reviewer} ``Microeconometrics and MATLAB'', by Abi Adams, Damian Clarke \& Simon Quinn, Oxford University Press, (forthcoming 2015).
\item \textbf{Manuscript reviewer} The Official Journal of The Society for Computational Economics, The R Journal, Social Networks, SUNBELT Conference (2016), International Conference on Computational Social Science (2019).
\item \textbf{Misc} Founder of the R Users Group in Chile (2013), co-organizer of the East LA R User Group (LAERUG).
%\item \textbf{Honorable Mention} (Posters Sesion. Work: \emph{Introducing Parallel: Stata Module for Parallel Computing}) given by the Chilean Economics Society during its 2012 annual meetting.
%\item \textbf{Honour Scholarship} given by Adolfo Ib\'a\~nez University for completing undergrad and graduate studies (2006-2010).
%\item \textbf{Software workshop, 2010.} \emph{Co-founder} of the workshop thaught by Economics and PP Masters's Students at Adolfo Ib\'a\~nez University in order to introduce grad students into scholar research software (\LaTeX, \emph{R}, Stata, etc.).
\end{itemize}

\bigskip

% Footer
\begin{center}
 \begin{footnotesize}
   last update: \today \\
   \href{\footerlink}{\texttt{\footerlink}}
 \end{footnotesize}
\end{center}

\end{document}

